---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# kaggling

<!-- badges: start -->
<!-- badges: end -->

The goal of kaggling is to ...

## Installation

You can install the development version of kaggling like so:

``` r
remotes::install_github("heike/kaggling")
```

This package relies on a valid installation of `kaggle` (python 3 based package). 
This includes a Kaggle account and authorization tokens for the API. 
Refer to https://github.com/Kaggle/kaggle-api for installation instructions.


## Basic Usage


Load the package functionality:

```{r example}
library(kaggling)
```

The main functionality is centered on searching for data sets using a search key word:

```{r}
iris <- search_kaggle("iris")
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
