---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# kaggling

<!-- badges: start -->
<!-- badges: end -->

The goal of kaggling is to get an overview of kaggle datasets and their provenance.

## Installation

You can install the development version of kaggling like so:

``` r
remotes::install_github("heike/kaggling")
```

This package relies on a valid installation of `kaggle` (python 3 based package). 
This includes a Kaggle account and authorization tokens for the API. 
Refer to https://github.com/Kaggle/kaggle-api for installation instructions.


## Basic Usage


Load the package functionality:

```{r example}
library(kaggling)
```

### Search kaggle

The main functionality is centered on searching for data sets using a search key word:

```{r cache=TRUE}
ames <- search_kaggle("ames iowa housing")
dim(ames)
```
Kaggle hosts `r nrow(ames)` data sets that are found as a result of a search on 'ames iowa housing'.


```{r}
head(ames)
```
```{r message=FALSE}
library(tidyverse)

# the majority of the datasets has a size of about 200 KB. 
ames %>% mutate(
  size = parse_number(size)
) %>% ggplot(aes(x = size)) + geom_histogram()
```


### Get Meta information 

The data set identifier is stored in the variable `ref`. 

```{r}
ames$ref[1]
```
Meta information is extracted from kaggle using the function `get_meta`.

```{r}
# single set of meta information
get_meta(ames$ref[1])$meta
```
`get_meta` expands the dataset by the list variable `meta`. 

```{r cache=TRUE}
ames <- get_meta(ames)
```

```{r}
ames_meta <- ames %>% tidyr::unnest(cols=meta, names_sep="_")

# There is a plethora of licenses involved
ames_meta %>% count(meta_licenses.name)
```

<!--
Unfortunately, neither of these 35 very similar looking data files mention ISU StatCom or Dean De Cock's 2011 paper [Ames, Iowa: Alternative to the Boston Housing Data as an End of Semester Regression Project](https://www.tandfonline.com/doi/epdf/10.1080/10691898.2011.11889627?needAccess=true) in the Journal of Statistics Education.

https://jse.amstat.org/v19n3/decock/AmesHousing.txt
https://jse.amstat.org/v19n3/decock/DataDocumentation.txt

-->
